---
title       : mtCars prediction app
subtitle    : Developing Data Products course project
author      : jamesmcm
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## mtCars prediction App

* The mtCars prediction app lets you predict the MPG of a car given its weight (in 1000 lbs)

* https://jamesmcm.shinyapps.io/myapp/

* It uses the mtCars data with a linear model

* The app is hosted on ShinyApps.io 

* ShinyApps.io allows free hosting of Apps written in R with Shiny.

---

## Model

* The model is:

```{r}
library(datasets)
data(mtcars)
lm(mpg~wt, mtcars)
```

---

## Plot of data

* The data looks as follows:

``` {r, echo=FALSE}
  library(ggplot2)
    ggplot(mtcars, aes(x=wt, y=mpg)) +
      geom_point(shape=1) +    # Use hollow circles
       geom_smooth(method=lm) +
      ggtitle("Fit of MPG vs. Weight for mtcars data") +
     xlab("Weight (1000 lbs)") +
    ylab("Miles per US Gallon")
```

---

### Conclusion


* Try out the mtCars prediction app today

* The app is hosted on ShinyApps.io at:
https://jamesmcm.shinyapps.io/myapp/

* This pitch was written in RMarkdown with Slidify

